% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
%
\newcommand{\student}{\textsuperscript{*}}
\newcommand{\studentnote}{%
  \par\vspace{1ex}% some space before note
  {\small\noindent * = Student co-author at time of writing.}%
}

% Note that i've heavily modified this template (me being Patrick Button)
% So it's no longer the exact one created by Jason Blevins.

\documentclass[letterpaper]{article}

%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{alltt}
\usepackage{multicol}
%\usepackage[ocgcolorlinks]{hyperref}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue, ocgcolorlinks]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%
\definecolor{goldenyellow}{rgb}{1.0, 0.87, 0.0}
\definecolor{darkpink}{rgb}{0.91, 0.33, 0.5}
\usepackage[mdyy]{datetime}
\usepackage{fontawesome}

\usepackage{textcomp}

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\bfseries\scshape}{}{0em}{}[] % Text formatting of sections
\titlespacing{\section}{0pt}{1pt}{1pt} % Spacing around sections

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\fontfamily{ppl}\selectfont 
%\usepackage{palatino}
\usepackage[T1]{fontenc}

%\usepackage[sc,osf]{mathpazo}
%\usepackage{pslatex}
% Set your name here
\def\name{Hussain Hadah}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties

\hypersetup{
  colorlinks = true,
  urlcolor=blue!50!black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae of Hussain Hadah},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.3in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
%\pagestyle{myheadings}
\markright{\today \rm}
\thispagestyle{empty}


% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Print name centered and bold:
\centerline{\huge \bf \name}
%\titlerule

\begin{center}
   \hspace{0.5mm} Pronouns: He/Him \href{https://www.mypronouns.org/}{\faQuestionCircleO}  
\\    
\hspace{0.5mm} Citizenship: United States of America
\\
\faEnvelopeO \hspace{0.5mm} \href{mailto:hhadah@tulane.edu}{hhadah@tulane.edu} \rm  \hspace{0.5mm} \faGlobe \hspace{0.5mm} \href{https://www.hussainhadah.com/}{www.hussainhadah.com} 
\href{https://www.linkedin.com/in/hussain-hadah/}{\faLinkedinSquare} \href{https://github.com/hhadah}{\faGithub} 
\\ The Murphy Institute, Tulane University \\
Caroline Richardson Building \\
62 Newcomb Place, Suite 118 \\
New Orleans, LA 70118\\
  
\end{center}

%\singlespacing

\section*{Education}
\vspace{2 mm}
\begin{itemize}
  \item {\makebox[1.8cm]{2023.\hfill}}Ph.D. Economics, University of Houston. \\{\makebox[1.8cm]{\hfill}}Dissertation \textit{“Essays on Hispanic Identity”}. \\{\makebox[1.8cm]{\hfill}}Committee: Chinhui Juhn (co-chair), Vikram Maheshri (co-chair), Yona Rubinstein, and \\{\makebox[1.8cm]{\hfill}}Willa Friedman.
  \item {\makebox[1.8cm]{2020.\hfill}}M.A. in Economics. University of Houston. 
  \item {\makebox[1.8cm]{2017.\hfill}}B.S. in Economics.  Arizona State University. \\{\makebox[1.8cm]{\hfill}}\textit{Minors:} Mathematics and International Relations. \\{\makebox[1.8cm]{\hfill}}\textit{Honors:} Summa Cum Laude, Phi Beta Kappa.
\end{itemize}
\vspace{2 mm}

\section*{Academic Positions}
\vspace{2 mm}
\begin{itemize}
  \item {\makebox[1.8cm]{2023-present. \hfill}} Postdoctoral Fellow. Department of Economics, School of Liberal Arts, \\{\makebox[1.8cm]{\hfill}} and the Murphy Institute. Tulane University.
  \item {\makebox[1.8cm]{2025-present. \hfill}} Consultant. Research and Innovation for Social and Economic Inclusion (RISEI) \\{\makebox[1.8cm]{\hfill}} Lab, Northwestern University.
\end{itemize}
\vspace{2 mm}

\section*{Research Areas}
\vspace{2 mm}
\begin{itemize}
\item {\makebox[2.5cm]{\textbf{Econ. Fields:}\hfill}} Labor, Education, Urban, Health
\item {\makebox[2.5cm]{\textbf{Topics:}\hfill}} Economics of discrimination, Identity, Race, Ethnicity, Peer effects, Mental health, \\{\makebox[2.5cm]{\hfill}} Audit Studies, Policy Evaluation
\item \textit{You can read my detailed research statement \href{https://hhadah.github.io/statements/Hadah_Research.pdf}{here}.}
\end{itemize}
\vspace{2 mm}

\section*{Publications}
\vspace{2 mm}
\begin{itemize}
      \item Hadah, Hussain. (2025). ``The Impact of Hispanic Last Names on Labor Market and Educational \\  
    \makebox[4mm]{} Outcomes.'' \textit{Journal of Economics, Race, and Policy}. \href{https://doi.org/10.1007/s41996-025-00177-3}{DOI: 10.1007/s41996-025-00177-3}
    \item  Hadah, Hussain. (2024). ``The effect of racial and ethnic attitudes on Hispanic identity in the \\ 
    \makebox[4mm]{} United States.'' \textit{Southern Economic Journal}. \href{https://doi.org/10.1002/soej.12749}{DOI: 10.1002/soej.12749}.
\end{itemize}
\vspace{2 mm}

\section*{Revise and Resubmit}
\vspace{2 mm}
\begin{itemize}
  \item Hadah, Hussain. ``The Effect of Anti-Asian Attitudes on Asian Identity in the U.S.'', \textit{Revise and Resubmit} \\{\makebox[4mm]{\hfill}} \textit{Journal of Policy Analysis and Management} [\href{https://hhadah.github.io/asian-identity-attrition/my_paper/submit_preprint.pdf}{Link}]. 
\end{itemize}
\vspace{2 mm}
\section*{Working Papers}
\vspace{2 mm}
\begin{itemize}
  \item Hadah, Hussain. ``Peer Effects in Adolescent Mental Health'' [\href{https://hhadah.github.io/Depression_Idea/my_paper/Hadah-Peer-Effect-Depression.pdf}{Link}].
  \item Hadah, Hussain and Bariş Alan\student. ``Democratic Institutions and Their Effect on Ethnic Favo-\\{\makebox[4mm]{\hfill}} ritism: Evidence from Saharan Africa'' [\href{https://dx.doi.org/10.2139/ssrn.4566225}{Link}].
  \item Hadah, Hussain and Gael Compta\student. ``The Effects of Waiting Periods on Firearm Suicides in the \\{\makebox[4mm]{\hfill}} U.S.'' [\href{https://dx.doi.org/10.2139/ssrn.5383500}{Link}]
  \item Hadah, Hussain ``Immigration Enforcement, Sanctuary Cities, and Rising Hispanic Suicide Rates'' [\href{https://hhadah.github.io/sc-hispanic-adult-suicide/my_paper/sc_and_hispanic_children_suicide.pdf}{Link}]
  \item Denteh, Augustine and Hussain Hadah. ``Immigration Enforcement and Hispanic Identity.'' [\href{https://hussainhadah.com/research/working-papers/hadah-denteh/immigration_enforcement_hispanic.pdf}{Link}]
\end{itemize}
\vspace{2 mm}

\section*{Works in Progress}
\vspace{2 mm}
\begin{itemize}
\item Button, Patrick, Hussain Hadah, Javiera Selman, Cathy Balfe\student, and Tran Nguyen-\\{\makebox[4mm]{\hfill}}Phuong\student. ``Sexual orientation discrimination in mortgage lending: an audit field experiment.''

\item Patrick Button, Hadah, Hussain, Douglas Harris, and Barbara Lundebjerg\student. ``Parent’s Choice or School’s \\{\makebox[4mm]{\hfill}} Choice?
Discrimination Against Students in Admission to Private, Charter, and Traditional Public \\{\makebox[4mm]{\hfill}} Schools.'' \textit{Funded by \$140,747 grant from JPAL}

\item Button, Patrick, Clare Daniel, Hussain Hadah, 
Julie Hernandez, Mirya Holman, and Anna Mahoney. 
\\{\makebox[4mm]{\hfill}}``Auditing Crisis
 Pregnancy Centers: Racial biases, misinformation, 
and the misallocation \\{\makebox[4mm]{\hfill}}government resources.'' (tentative title)

\item Hadah, Hussain. ``Endogenous Hispanic Identity and Ethnic Gaps in the U.S''. (Using census \\{\makebox[4mm]{\hfill}} administrative data with the RDC).


\end{itemize}


\section*{Grants}

\vspace{2 mm}
\textit{Grants Received, External} \\
\begin{itemize}
  \item {\makebox[1.8cm]{2025.\hfill}} {\makebox[1.8cm]{\$140,747 \hfill}}J-PAL Social Policy Research Initiative / Racial Equity Special Topic \\{\makebox[17mm]{\hfill}} RFP - ”Parent’s Choice or School’s Choice? Discrimination Against Students in \\{\makebox[17mm]{\hfill}} Admission to Private, Charter, and Traditional Public Schools” with \\{\makebox[17mm]{\hfill}} Patrick Button and Doug Harris \\{\makebox[17mm]{\hfill}} (Co-PIs), and Barbara Lundebjerg\student
\end{itemize}

\textit{Invited for a Full Proposal or Under Review} \\
\begin{itemize}
  \item {\makebox[1.8cm]{2025.\hfill}} {\makebox[1.8cm]{\$126,437 \hfill}}Russell Sage Foundation - ”Parent’s Choice or School’s Choice? Discrimination \\{\makebox[17mm]{\hfill}} Against Students in Admission to Private, Charter, and Traditional Public Schools” \\{\makebox[17mm]{\hfill}}  with Patrick Button and Doug Harris (Co-PIs,) and Barbara Lundebjerg\student
\end{itemize}

\vspace{2 mm}
\textit{Internal Funding} \\
\begin{itemize}
  \item {\makebox[1.8cm]{2025.\hfill}} {\makebox[1.8cm]{\$2,500\hfill}}Connolly Alexander Institute for Data Science (CAIDS) at Tulane University.
\end{itemize}
\vspace{2 mm}
\begin{itemize}
  \item {\makebox[1.8cm]{2023.\hfill}} {\makebox[1.8cm]{\$3,000\hfill}}Seed Grant. Murphy Institute. Tulane University.
\end{itemize}
\studentnote
\section*{Conferences and Seminar Presentations (Including Scheduled)}
\vspace{2 mm}
\begin{itemize}
% \item (Scheduled) Universidad Adolfo Ibáñez (10/13); 28th Annual LACEA Meeting 2023 (11/16)
\item {\makebox[1.8cm]{2025.\hfill}}The Defense Resources Management Institute (DRMI), Monterey, CA; Northwestern’s School \\{\makebox[1.8cm]{\hfill}}of Education and Social Policy (SESP); Tenth Annual Conference on Network Science in  \\{\makebox[1.8cm]{\hfill}}Economics, Stanford University, CA; American Society of Health Economists Annual \\{\makebox[1.8cm]{\hfill}}Conference, Nashville; J-PAL Racial Equity Design with Reach (DWR); Association for \\{\makebox[1.8cm]{\hfill}}Public Policy Analysis \& Management (APPAM), Seattle; Southern Economic Association \\{\makebox[1.8cm]{\hfill}}Conference, Tampa, FL; NBER Race and Stratification Working Group, Cambridge, MA.
\item {\makebox[1.8cm]{2024.\hfill}}Murphy Institute Health Policy Seminars; Southern Economic Association \\{\makebox[1.8cm]{\hfill}}Conference, DC.
\item {\makebox[1.8cm]{2023.\hfill}}Stata Texas Empirical Microeconomics Conference; Tulane University; European Society for \\{\makebox[1.8cm]{\hfill}}Population Economics (ESPE); Southern Economic Association \\{\makebox[1.8cm]{\hfill}}Conference, New Orleans ($\times$ 2).
\item {\makebox[1.8cm]{2021.\hfill}}\href{https://www.southerneconomic.org/session-details/?conferenceId=7&eventId=3353}%
{Southern Economic Association}, Houston, Texas
\item {\makebox[1.8cm]{2020.\hfill}}\href{https://cega.berkeley.edu/initiative/working-group-in-african-political-economy/}%
{Working Group in African Political Economy}, University of  California, Berkeley (\textit{workshop}).

\end{itemize}

\vspace{2 mm}

\section*{Academic Honors}
\vspace{2 mm}
\begin{itemize}
\item {\makebox[2.1cm]{2024.\hfill}} Best Graduate Student Poster, Stata Texas Empirical Microeconomics Conference
\item {\makebox[2.1cm]{2017--2023.\hfill}} Doctoral Student Tuition Fellowship, University of Houston. 
\item {\makebox[2.1cm]{2017-present.\hfill}} The Phi Beta Kappa Society. 
\item {\makebox[2.1cm]{2017.\hfill}} Arizona State University Grant. 
\item {\makebox[2.1cm]{2016--2017.\hfill}} Graduated Summa Cum Laude, 4.00 GPA. BS in Economics. Arizona State University. 
\item {\makebox[2.1cm]{2016--2017.\hfill}} Dean's List, Arizona State University. 
\end{itemize}
\vspace{2 mm}

\section*{Teaching}
\vspace{2 mm}

You can read my detailed teaching statement \href{https://hhadah.github.io/statements/Hadah_Teaching.pdf}{here}.

\textit{Instructor}
\begin{itemize}
\item {\makebox[3.0cm]{Fall 2025.\hfill}}Urban Economics, Undergraduate. Tulane University.
\item {\makebox[3.0cm]{Spring 2024.\hfill}}Urban Economics, Undergraduate. Tulane University.
\item {\makebox[3.0cm]{Summer 2022.\hfill}}Principles of Microeconomics. University of Houston.
\item {\makebox[3.0cm]{Spring 2022.\hfill}}Principles of Microeconomics. University of Houston.
\item {\makebox[3.0cm]{Summer 2021.\hfill}}Principles of Microeconomics. University of Houston.

\end{itemize}
\textit{Teaching Assistant}
\begin{itemize}
\item {\makebox[1.8cm]{2022-2023.\hfill}}Political Economy. Gergely Ujhelyi. University of Houston.
\item {\makebox[1.8cm]{2021--2022.\hfill}}Intermediate Microeconomics. Piruz Saboury. University of Houston.
\item {\makebox[1.8cm]{2020--2021.\hfill}}Principles of Microeconomics. Joel Melendez Lugo. University of Houston.

\end{itemize}
\vspace{2 mm}
\studentnote
\section*{Research Experience}
\vspace{2 mm}
\textit{Research Assistant}
\begin{itemize}
\item {\makebox[5.0cm]{May 2021--August2021.\hfill}}\href{https://vmaheshri.github.io/}{Vikram Maheshri}.
\item {\makebox[5.0cm]{June 2020--May 2022.\hfill}}\href{https://www.uh.edu/class/economics/people/current-faculty/steve/}{Steve Craig}.
\item {\makebox[5.0cm]{August 2019--August 2020.\hfill}}\href{https://sites.google.com/site/vegardmokleivnygaard/}{Vegard Mokleiv Nygaard}.
\end{itemize}
\vspace{2 mm}

\section*{Previous Employment}
\vspace{2 mm}
\begin{itemize}
\item {\makebox[1.8cm]{2017-2018.\hfill}}Data Analyst and Researcher. Congressional Campaign for Alex Triantaphyllis for Congress.
\end{itemize}
\vspace{2 mm}

\section*{Languages}
\vspace{2 mm}
{\makebox[2.3cm]{\hfill}}English (native), Arabic (native), French (beginner), Spanish (beginner).
\vspace{2 mm}


\section*{Programming and Software Experience}
\vspace{2 mm}
{\makebox[2.3cm]{\hfill}}R, Stata, Python, QGIS, \LaTeX.
\vspace{2 mm}

\section*{Referee Activity}
\vspace{2 mm}
{\makebox[2.3cm]{\hfill}}\textit{Journal of Economics, Race, and Policy}.
\vspace{2 mm}

\section*{Additional Qualifications}
\vspace{2 mm}
{\makebox[2.3cm]{\hfill}}\textit{Special Sworn Status} with the U.S. Census Bureau.
\vspace{2 mm}

\section*{Advising and Mentoring}

\textit{Ph.D. Students}
\vspace{2 mm}
\begin{itemize}
\item {\makebox[1.8cm]{2024-present.\hfill}} Rayna Gasik, School of Public Health and Tropical Medicine.
\item {\makebox[1.8cm]{2024-present.\hfill}} Baris Alan, Political Science.
\end{itemize}
\vspace{2 mm}
\textit{Undergraduate Students}
\vspace{2 mm}
\begin{itemize}
\item {\makebox[1.8cm]{2025-present.\hfill}} Anjali Hunt-Kasturi.
\end{itemize}
\section*{References}

\parbox[t]{0.32\textwidth}{
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill
{\textit{Patrick Button }}  \\\\
Associate Professor \\
Department of Economics \\
Executive Director \\
The Connolly Alexander Institute \\
for Data Science (CAIDS) \\
{Tulane University}\\ 
{\href{mailto:pbutton@tulane.edu}{pbutton@tulane.edu}}
\end{tabbing}}
\hfill
\parbox[t]{0.32\textwidth}{
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill
{\textit{Chinhui Juhn }} \\\\
Professor \\
Department of Economics \\
{University of Houston}\\ 
{\href{mailto:cjuhn@uh.edu}{cjuhn@uh.edu}}
\end{tabbing}}
\hfill
\parbox[t]{0.32\textwidth}{ 
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill
{\textit{Vikram Maheshri} } \\\\
Associate Professor \\
Department of Economics \\
{University of Houston}\\ 
{\href{mailto:vmaheshri@gmail.com}{vmaheshri@gmail.com}}
\end{tabbing}}

\vspace{0.7cm}

\noindent
\parbox[t]{0.32\textwidth}{ 
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill
{\textit{Douglas Harris} } \\\\
Professor and Department Chair \\
Department of Economics \\
{Tulane University}\\ 
{\href{mailto:dharri5@tulane.edu}{dharri5@tulane.edu}}
\end{tabbing}}
\hspace{0.1\textwidth}
\parbox[t]{0.32\textwidth}{ 
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill
{\textit{Gary A Hoover} } \\\\
Professor  \\
Department of Economics \\
Executive Director \\
The Murphy Institute \\
{Tulane University}\\ 
{\href{mailto:ghoover@tulane.edu}{ghoover@tulane.edu}}
\end{tabbing}}

\enlargethispage{-10mm}  % Adjust as necessary
% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{https://hussainhadah.com/cv/}{\texttt{https://hussainhadah.com/cv/}}
  \end{footnotesize}
\end{center}

\end{document}
